From Reversible Programs to \\ Univalent Universes and Back

### 2021-07-05 Pi+/paper/finite.tex
Revise section 4 and cut text

Before, the only way to decide the equality of two elements in a group was to compute and check them on the nose, but in
a group presentation, this is reduced to a \emph{word problem}, that is, deciding whether one word -- a representative
of the equivalence class of the group's elements, can be reduced to another word, using the group's relations. However,
these equations are not directed, so it is not always possible to construct a well-behaved rewriting system. In general,
the word problem for groups is known to be undecidable.\jk{Example?}\todo{Examples: empty relation, full relation, van
  Kampen of $\pi_{1}$}

@@

This construction is called a Coxeter presentation of $\Sn$. Writing it formally, we encode the rules discussed above
using a relation $\cox$ on $\List[\Fin[n]]$, and then take its congruence closure $\cox*$.

\begin{definition}[$\cox : {\List[\Fin[n]]} \to {\List[\Fin[n]]} \to {\UU}$]
  \begin{align*}
    \cancel
     & : \forall n \to (n \cons n \cons \nil) \cox \nil                                                     \\
    \swap
     & : \forall k, n \to (\suc[k] < n) \to (n \cons k \cons \nil) \cox (k \cons n \cons \nil)              \\
    \braid
     & : \forall n \to (\suc[n] \cons n \cons \suc[n] \cons \nil) \cox (n \cons \suc[n] \cons n \cons \nil) \\
  \end{align*}
\end{definition}
\begin{definition}[$\cox* : {\List[\Fin[n]]} \to {\List[\Fin[n]]} \to {\UU}$]
  \begin{align*}
    \reflr{\cox}
     & : \forall w \to w \cox* w                                                                                                           \\
    \symr{\cox}
     & : \forall w_{1}, w_{2} \to w_{1} \cox* w_{2} \to w_{2} \cox* w_{1}                                                                  \\
    \transr{\cox}
     & : \forall w_{1}, w_{2}, w_{3} \to  w_{1} \cox* w_{2} \to w_{2} \cox* w_{3} \to w_{1} \cox* w_{3}                                    \\
    \congrf{\cox}{\append}
     & : \forall w_{1}, w_{2}, w_{3}, w_{4} \to  w_{1} \cox* w_{2} \to w_{3} \cox* w_{4} \to w_{1} \append w_{3} \cox* w_{2} \append w_{4} \\
    \relr{\cox}
     & : \forall w_{1}, w_{2} \to w_{1} \cox w_{2} \to w_{1} \cox* w_{2}                                                                   \\
  \end{align*}
\end{definition}

@@

\begin{figure}
  \[
    \begin{tikzpicture}
      \pic[local bounding box=my braid,braid/.cd,
        number of strands = 5,
        thick]
      {braid={s_4, s_3, s_2, s_1}};
    \end{tikzpicture}
  \]
  \caption{Braiding diagram for $0 \downf 4$}
  \label{fig:downf}
\end{figure}

@@

Constructors $\longcancel$ and $\longswap$ correspond directly to the appropriate constructors of $\cox$ and can be
visualised in the same way as before. The remaining constructor uses the helper function to exchange the order of a long
sequence of transpositions and a single transposition afterwards. For example, for $n = 2$ and $k = 3$, it allows for
the reduction $[6, 5, 4, 3, 2, 6] \longcox* [5, 6, 5, 4, 3, 2]$ (for the appropriate braid diagram,
see~\cref{fig:longcox}).
\begin{figure}
  \[
    \begin{tabular}{m{0.4\linewidth}m{0.1\linewidth}m{0.4\linewidth}}
      \begin{center}
        \begin{tikzpicture}
          \pic[local bounding box=my braid,braid/.cd,
            number of strands = 6,
            thick]
          {braid={s_5, s_4, s_3, s_2, s_1, s_5}};
        \end{tikzpicture}
      \end{center}
       &
      \(\xlongrightarrow[]{\longbraid}\)
       &
      \begin{center}
        \begin{tikzpicture}
          \pic[local bounding box=my braid,braid/.cd,
            number of strands = 6,
            thick]
          {braid={s_4, s_5, s_4, s_3, s_2, s_1}};
        \end{tikzpicture}
      \end{center}
    \end{tabular}
  \]
  \caption{Braiding diagram for $\longcox$ with $n = 0$ and $k = 3$}
  \label{fig:longcox}
\end{figure}

@@

Despite the increased complexity of the generators, the rewriting system $(\List[\Fin[n]],\longcox*)$ has the properties
we desire. It satisfies confluence, that is, the Church-Rosser (diamond) property, and it is strongly normalising,
because it produces a unique irreducible normal form. We follow the terminology
of~\cite{krausCoherenceWellFoundednessTaming2020} to state our results formally.~\vc{check!}

@@

The modified form of the Coxeter relations are unwieldy and difficult to prove properties about by induction. However,
we can use the following observation to be able to use the more standard $\cox*$ relation.~\todo{Check Huet's paper for
  this property.}

@@

The type $\Sn$ is defined as the set-quotient of $\List[\Fin[n]]$ by $\cox*$,

@@

Note that this relation $\cox*$ is not $\hProp$-valued, that is, $w \cox* v$ is not a proposition because reductions are
not unique. Because of this, the quotient $\Sn$ is not effective, that is, $\quotrel : w \cox* v \to q(w) \id q(v)$ is
not an equivalence. We could truncate the relation to change this, but then the codomain of $\normf$ also needs to be
truncated.

We could also define equivalence classes on $\List[\Fin[n]]$ to be those terms that have the same normal form. Using the
$\normf$ function, we could define a new relation $(w \approx v) \defeq (\normf(w) \id \normf(v))$ which is
$\hProp$-valued, and quotient $\List[\Fin[n]]$ by $\approx$. Using the properties of the rewriting system we proved, we
make a few observations.

\begin{proposition}
  \leavevmode
  \begin{enumerate}
    \item $\normf$ splits into a section-retraction pair, that is, we have ${\List[\Fin[n]]} \xrightarrow{s} \Sn[n]
            \xrightarrow{r} {\List[\Fin[n]]}$ such that $s \comp r \htpy \normf$ and $r \comp s \htpy \idfunc_{\Sn[n]}$.
    \item \(\im{\quotinc} \eqv \Sn \eqv \im{\normf} \).
  \end{enumerate}
\end{proposition}

@@

\begin{proposition}
  \leavevmode
  \begin{enumerate}
    \item There is a group structure on $\Sn$, where the identity element is $\nil$, multiplication is given by list
          append, and inverse is given by list reversal.
    \item $\Sn$ is equivalent to the group presented by generators $\Fin[n] + \Fin[n]$ with the relations given by the
          normal closure of $\cox*$ extended to $\List(\Fin[n] + \Fin[n])$ along the codiagonal map $\nabla_{A} : A + A
            \to A$.
  \end{enumerate}
\end{proposition}

We set out to solve the word problem for $\Sn$. To decide if two words in $\List[\Fin[n]]$ are equal, we simply have to
compute their normal forms using $\normf$ and check if they're equal on the nose. If they do, they correspond to the
same permutation.

@@

To prove the equivalence between $\Aut[\Fin[n]]$ and $\Sn[n]$, we will need to define functions back and forth between
the two types. The terms in $\Sn$ can be identified with equivalence classes of terms in $\List[\Fin[n]]$ with respect
to the Coxeter relation $\cox*$. The easiest way to define a function out of this presentation is to define it on the
representatives. We know that these are the unique normal forms in the set-quotient given by $\quotinc \comp \normf$,
but now we will describe what these representatives exactly look like, using an encoding called Lehmer
codes~\cite{lehmerTeachingCombinatorialTricks1960}.

There are many ways to represent permutations, e.g. inversions, or cycles, or matrices. Lehmer codes are known in
Combinatorial Analysis~\cite{bellmanCombinatorialAnalysis1960} where they are sometimes called "subexcedant sequences",
or "factoriadics", which give the factorial number system. They are a particularly convenient way of representing
permutations on a computer, partly because they are bitwise-optimal: for any $n : \Nat$, the type $\Lehmer[n]$ hass the cardinality $\fac{n}$, and has an easy to consttuct bijection with $\Aut[\Fin[n]]$. .

Formally, we define $\Lehmer[n]$ to be an $n+1$-element tuple, where the position $k \leq n$ stores an element of $\Fin[k]$. Since
the 0-th position is trivial, in practice, it is ignored, and the sequence starts at
1~\cite{duboisTestsProofsCustom2018,vajnovszkiNewEulerMahonian2011}.\todo{There are more examples - listed
  in~\cite{duboisTestsProofsCustom2018}}. We can then define $\Lehmer$ in two equivalent ways, by a simple recursion on
$\Nat$, or as a type family generated by two constructors.

\begin{definition}[$\Lehmer : \Nat \to \UU$]
  \begin{gather*}
    \begin{aligned}
      \Lehmer[\zero]   & \defeq \Fin[\suc[\zero]]                     \\
      \Lehmer[\suc[n]] & \defeq \Fin[\suc[\suc[n]]] \times \Lehmer[n]
    \end{aligned}
    \qquad
    \begin{aligned}
      \lzero & : \Lehmer[\zero]                                                     \\
      \lsuc  & : \forall n, r, (r \leq \suc[n]) \to \Lehmer[n] \to \Lehmer[\suc[n]]
    \end{aligned}
  \end{gather*}
\end{definition}

\todo{Explain why the two definitions are equivalent?}

For a permutation $\sigma : \Aut[\Fin[n]]$, for any element $i: \Fin[n]$, we can define the inversion count of $i$ as
the number of smaller elements appearing after it in the permutation.

\todo{typify}
\begin{definition}
  Given a permutation $\sigma : \Aut[\Fin[n]]$, the inversion count of $k: \Fin[n]$ is given by
  \[ |\Set{j < i | \sigma(j) > \sigma(i)}|. \]
\end{definition}

It turns out that from knowing just the inversion counts for all the elements, one can reconstruct the starting
permutation. Also, observe that the inversion count for element $i$ is guaranteed to be smaller than $i$, thus fitting
in the $i$-th place of a Lehmer code tuple. As an example, consider the following tabulated presentation of a
permutation of $\Fin[5]$.

@@

The inversion count for $\el{0}$ is 0 (because there are no smaller elements at all), for $\el{1}$ is 1 (because of
$\el{0}$ appearing after), for $\el{2}$ is 2 (because of $\el{0}$ and $\el{1}$), for $\el{3}$ is 0 (because it comes
last in the sequence), and for $\el{4}$ is 2 (because of $\el{3}$ and $\el{0}$). Thus, the Lehmer code for the permutation $\sigma$
is the 5-tuple $l = (0, 1, 2, 0, 2)$.

@@

Writing formally, to turn a code into a permutation written in the Coxeter presentation, we define a function
$\immersion$. As described above, the number $r$ at position $k$ in the tuple describes how many inversions the element
$\el{k}$ has. Thus, we need to perform $r$ many adjacent transpositions to get to the desired position, which is given
by $(\suc[n] - r) \downf r$.

@@

As an example, let us look at the code $c = (4, 3, 2, 1, 0)$. The list $\immersion(c)$ is then going to be $[0, 1, 0, 2,
      1, 0, 3, 2, 1, 0, 4, 3, 2, 1, 0]$. It is a concatenation of a sequence of decreasing lists. Where could a reduction
happen? First, it can't happen inside any of the decreasing components: $\longcancel$ requires repeating elements,
$\longswap$ acts when a smaller number precedes a larger one, and $\longbraid$ has a non-monotone sequence on the left.
This leaves the case of a reduction happening on a fragment that borders two subsequences. Again, $\longcancel$ requires
two equal consecutive numbers, which have to be the last one in some decreasing sequence and the first one in the next
one. But the first number in a sequence is always larger than every number in the sequence before it - which also shows
why $\longswap$ cannot happen. The remaining case of $\longbraid$ is proven on similar grounds, since it requires the
number appearing after the decreasing sequence to be equal to the first one in the sequence.

Using this idea, we can show that the function $\immersion$ gives an equivalence betweeen $\Lehmer[n]$ and
$\im{\normf}$.

@@

We also established an equivalence between $\im{\normf}$ and $\Sn$, which gives the following.

\begin{proposition}~\label{prop:sn-im-lehmer-equiv}
  For all $n : \Nat$, \( \Sn \eqv \im{\normf} \eqv \Lehmer[n] \).
\end{proposition}

@@

Finally, it is time to complete our goal of characterising the permutation groups. Having produced a Lehmer code by
normalising words in $\Sn$, we need to run it to produce a concrete bijection of finite sets, and, given a bijection
between finite sets, we need to encode it as a Lehmer code. We will prove that these maps construct an equivalence
between the types $\Lehmer[n]$ and $\Aut[\Fin[\suc[n]]]$.

@@

\begin{proof}
  The first and second propositions follow from simply constructing the bijections using the decidable equality of
  $\Fin[n]$, and making sure to punch-in and punch-out the element $k$ at the right place.

@@

  For the other direction, if we are given a $k$ and a bijection $\pi$ between $\FinExcept{\suc[n]}[n]$ and
  $\FinExcept{\suc[n]}[n - k]$, we can extend $\pi$ to $\sigma : \Fin[\suc[n]] \eqv \Fin[\suc[n]]$ by inserting the
  element $n$ at the position $n - k$, resulting in the element $n$ having inversion count $k$.
\end{proof}

@@

By composing~\cref{prop:lehmer-aut-equiv} and~\cref{prop:sn-lehmer-fin-equiv}, we obtain the final equivalence.

>>>>

Before, the only way to decide the equality of two elements in a group was to evaluate and check them on the nose, but
in a group presentation, this is reduced to a \emph{word problem}, that is, deciding whether one word -- a
representative of the equivalence class of the group's elements, can be reduced to another word, using the group's
relations. However, these equations are not directed, so it is not always possible to construct a well-behaved rewriting
system. In general, the word problem for groups is known to be undecidable.\jk{Example?}\todo{Examples: empty relation,
  full relation, van Kampen of $\pi_{1}$}

@@

This construction is called a Coxeter presentation of $\Sn$. Writing it formally, we encode the rules discussed above
using a relation $\cox$ on $\List[\Fin[n]]$ (\cref{def:cox}), and then take its congruence closure $\cox*$
(\cref{def:coxstar}).

\begin{definition}[$\cox : {\List[\Fin[n]]} \to {\List[\Fin[n]]} \to {\UU}$]
  \label{def:cox}
  \begin{align*}
    \cancel
     & : \forall n \to (n \cons n \cons \nil) \cox \nil                                                     \\
    \swap
     & : \forall k, n \to (\suc[k] < n) \to (n \cons k \cons \nil) \cox (k \cons n \cons \nil)              \\
    \braid
     & : \forall n \to (\suc[n] \cons n \cons \suc[n] \cons \nil) \cox (n \cons \suc[n] \cons n \cons \nil) \\
  \end{align*}
\end{definition}

\begin{toappendix}
  \begin{definition}[$\cox* : {\List[\Fin[n]]} \to {\List[\Fin[n]]} \to {\UU}$]
    \label{def:coxstar}
    \begin{align*}
      \reflr{\cox}
       & : \forall w \to w \cox* w                                                                                                           \\
      \symr{\cox}
       & : \forall w_{1}, w_{2} \to w_{1} \cox* w_{2} \to w_{2} \cox* w_{1}                                                                  \\
      \transr{\cox}
       & : \forall w_{1}, w_{2}, w_{3} \to  w_{1} \cox* w_{2} \to w_{2} \cox* w_{3} \to w_{1} \cox* w_{3}                                    \\
      \congrf{\cox}{\append}
       & : \forall w_{1}, w_{2}, w_{3}, w_{4} \to  w_{1} \cox* w_{2} \to w_{3} \cox* w_{4} \to w_{1} \append w_{3} \cox* w_{2} \append w_{4} \\
      \relr{\cox}
       & : \forall w_{1}, w_{2} \to w_{1} \cox w_{2} \to w_{1} \cox* w_{2}                                                                   \\
    \end{align*}
  \end{definition}
\end{toappendix}

@@

\begin{figure}
  \[
    \begin{tikzpicture}
      \pic[local bounding box=my braid,braid/.cd,
        number of strands = 5,
        width = 0.6cm,
        height = 0.4cm,
        border height = 0.1cm,
        thick]
      {braid={s_4, s_3, s_2, s_1}};
    \end{tikzpicture}
  \]
  \caption{Braiding diagram for $0 \downf 4$}
  \label{fig:downf}
\end{figure}

@@

Constructors $\longcancel$ and $\longswap$ correspond directly to the appropriate constructors of $\cox$ and can be
visualised in the same way as before. The remaining constructor uses the helper function to exchange the order of a long
sequence of transpositions and a single transposition afterwards. For example, for $n = 2$ and $k = 3$, it allows for
the reduction $[6, 5, 4, 3, 2, 6] \longcox* [5, 6, 5, 4, 3, 2]$ (see~\cref{fig:longcox} for the braid diagram).

\begin{figure}
  \begin{tikzpicture}
    \pic[local bounding box=my braid,braid/.cd,
      number of strands = 6,
      width = 0.6cm,
      height = 0.4cm,
      border height = 0.1cm,
      thick] at (0, 0)
    {braid={s_5, s_4, s_3, s_2, s_1, s_5}};
    \node[font=\Huge] at (4, 1.3) {\(\rightarrow\)};
    \pic[local bounding box=my braid,braid/.cd,
      number of strands = 6,
      width = 0.6cm,
      height = 0.4cm,
      border height = 0.1cm,
      thick] at (5, 0)
    {braid={s_4, s_5, s_4, s_3, s_2, s_1}};
  \end{tikzpicture}
  \caption{Braiding diagram for $\longcox$ with $n = 0$ and $k = 3$}
  \label{fig:longcox}
\end{figure}

@@

Despite the increased complexity of the generators, the rewriting system $(\List[\Fin[n]],\longcox*)$ has the properties
we desire. It satisfies confluence, that is, the Church-Rosser (diamond) property, and it is strongly normalising, since
it produces a unique normal form. We follow the terminology
of~\cite*{huetConfluentReductionsAbstract1980a,krausCoherenceWellFoundednessTaming2020} to state our results
formally.~\vc{check!}

@@

The modified form of the Coxeter relations are unwieldy and difficult to prove properties about by induction. However,
we can use the following observation relating it to $\cox*$.~\todo{Check Huet's paper for this property.}

@@

Finally, we define the type $\Sn$ as the set-quotient of $\List[\Fin[n]]$ by $\cox*$,

@@

% Note that this relation $\cox*$ is not prop-valued, that is, $w \cox* v$ is not a proposition because reductions need
% not be unique. So, the quotient $\Sn$ is not effective, that is, $\quotrel : w \cox* v \to q(w) \id q(v)$ is not an
% equivalence. We could instead define equivalence classes on $\List[\Fin[n]]$ to be those terms that have the same normal
% form, using the $\normf$ function. Defining a new relation $(w \approx v) \defeq (\normf(w) \id \normf(v))$ which is
% prop-valued, we could quotient $\List[\Fin[n]]$ by $\approx$. This is an equivalent definition for $\Sn$.

Note that this relation $\cox*$ is not prop-valued, that is, $w \cox* v$ is not a proposition because reductions need
not be unique. So, the quotient $\Sn$ is not effective, that is, $\quotrel : w \cox* v \to q(w) \id q(v)$ is not an
equivalence. Using the $\normf$ function, we could instead define a new relation $\approx$ to equate those terms that
have the same normal form, $(w \approx v) \defeq (\normf(w) \id \normf(v))$. This relation is prop-valued, and we could
quotient $\List[\Fin[n]]$ by $\approx$, obtaining an equivalent definition for $\Sn$.

\begin{proposition}
  \leavevmode
  \begin{enumerate}
    \item $\normf$ splits into a section-retraction pair, that is, we have ${\List[\Fin[n]]} \xrightarrow{s} \Sn[n]
            \xrightarrow{r} {\List[\Fin[n]]}$ such that $s \comp r \htpy \normf$ and $r \comp s \htpy \idfunc_{\Sn[n]}$.
    \item \(\im{\quotinc} \eqv \Sn \eqv \im{\normf} \), where $\quotinc$ is the inclusion into the quotient.
  \end{enumerate}
\end{proposition}

@@

\begin{proposition}
  \leavevmode
  \begin{enumerate}
    \item There is a group structure on $\Sn$, where the identity element is $\nil$, multiplication is given by list
          append, and inverse is given by list reversal.
    \item $\Sn$ is equivalent to the group presented by generators $\Fin[n]$ with the relations given by $\cox*$
          extended to $\List(\Fin[n] + \Fin[n])$ along the codiagonal map $\nabla_{A} : A + A \to A$.
  \end{enumerate}
\end{proposition}

We set out to solve the word problem for $\Sn$. To decide if two words in $\List[\Fin[n]]$ are $\cox*$-equal, we simply
have to compute their normal forms using $\normf$. They correspond to the same permutation if and only if these normal
forms are equal.

@@

To prove the equivalence between $\Aut[\Fin[n]]$ and $\Sn[n]$, we will need to define functions back and forth between
the two types. The terms in $\Sn$ can be identified with equivalence classes of terms in $\List[\Fin[n]]$ with respect
to the Coxeter relation $\cox*$. The easiest way to define a function out of this presentation is to define it on the
representatives. We know that these are the unique normal forms in the set-quotient given by $\quotinc \comp \normf$,
but now we will explicitly describe what these representatives look like, using an encoding called Lehmer
codes~\cite{lehmerTeachingCombinatorialTricks1960}.

Lehmer codes are known in Combinatorial Analysis~\cite{bellmanCombinatorialAnalysis1960} where they are sometimes called
"subexcedant sequences", or "factoriadics", which give the factorial number system. They are a convenient way of
representing permutations on a computer, partly because they are
bitwise-optimal~\cite{bergerTeachingOrdinalPatterns2019a}.

Formally, we define $\Lehmer[n]$ to be an $n+1$-element tuple, where the position $k \leq n$ stores an element of
$\Fin[k]$. Since the 0-th position is trivial, in practice it is ignored, and the sequence starts at
1~\cite{duboisTestsProofsCustom2018,vajnovszkiNewEulerMahonian2011}.

\begin{definition}[$\Lehmer : \Nat \to \UU$]
  \begin{align*}
    \Lehmer[\zero]   & \defeq \Fin[\suc[\zero]]                     \\
    \Lehmer[\suc[n]] & \defeq \Fin[\suc[\suc[n]]] \times \Lehmer[n]
  \end{align*}
  % \begin{aligned}
  %   \lzero & : \Lehmer[\zero]                                                     \\
  %   \lsuc  & : \forall n, r, (r \leq \suc[n]) \to \Lehmer[n] \to \Lehmer[\suc[n]]
  % \end{aligned}
\end{definition}

Given a permutation $\sigma : \Aut[\Fin[n]]$, for any element $i: \Fin[n]$, we can define the inversion count of $i$ as
the number of smaller elements appearing after it in the permutation.

\begin{definition}
  Given a permutation $\sigma : \Aut[\Fin[n]]$, the inversion count of $k: \Fin[n]$ is given by
  \[ \invcount{i} = \#\Set{j < i | \sigma(j) > \sigma(i)}. \]
\end{definition}

From knowing just the inversion counts for all the elements, one can reconstruct the starting permutation. Also, observe
that $\invcount{i} < i$, thus fitting in the $i$-th place of a Lehmer code tuple. As an example, consider the following
tabulated presentation of a permutation of $\Fin[5]$.

@@

% The inversion count for $\el{0}$ is 0 (because there are no smaller elements at all), for $\el{1}$ is 1 (because of
% $\el{0}$ appearing after), for $\el{2}$ is 2 (because of $\el{0}$ and $\el{1}$), for $\el{3}$ is 0 (because it comes
% last in the sequence), and for $\el{4}$ is 2 (because of $\el{3}$ and $\el{0}$).

The Lehmer code for the permutation $\sigma$ is then the 5-tuple
\[
  l = (\invcount{0}, \invcount{1}, \invcount{2}, \invcount{3}, \invcount{4}) = (0, 1, 2, 0, 2)
\]

@@

Writing formally, to turn a Lehmer code into a word in $\Sn$, we define a function $\immersion$. As described above, the
number $r$ at position $k$ in the tuple describes how many inversions the element $\el{k}$ has. Thus, we need to perform
$r$ many adjacent transpositions to get to the desired position, which is given by $(\suc[n] - r) \downf r$.

@@

We can show that the function $\immersion$ gives an equivalence betweeen $\Lehmer[n]$ and $\im{\normf}$.

@@

\jk{Review:}
To see that Lehmer codes under $\immersion$ are normal with respect to $\longcox*$, let us look at the example code $c =
  (4, 3, 2, 1, 0)$. The list $\immersion(c)$ is then going to be $[0, 1, 0, 2, 1, 0, 3, 2, 1, 0, 4, 3, 2, 1, 0]$. It is a
concatenation of five decreasing lists. Where could a reduction happen?

First, it can't happen inside any of the decreasing components: $\longcancel$ requires repeating elements, $\longswap$
acts when a smaller number precedes a larger one, and $\longbraid$ has a non-monotone sequence on the left. This leaves
the case of a reduction happening on a fragment that borders two subsequences. Again, $\longcancel$ requires two equal
consecutive numbers, which have to be the last one in some decreasing sequence, and the first one in the next sequence.
But the first number in a sequence is always larger than every number in the sequence before it -- which also shows why
$\longswap$ cannot happen. The remaining case of $\longbraid$ follows similarly, since it requires the number appearing
after the decreasing sequence to be equal to the first one in the sequence.

% We also established an equivalence between $\im{\normf}$ and $\Sn$, which gives the following.
\begin{corollary}
  \label{prop:sn-im-lehmer-equiv}
  For all $n : \Nat$, \( \Sn \eqv \im{\normf} \eqv \Lehmer[n] \).
\end{corollary}

@@

Finally, it is time to complete our goal of characterising the permutation groups. Having produced a Lehmer code by
normalising words in $\Sn$, we need to run it to produce a concrete bijection of finite sets, and, given a bijection
between finite sets, we need to encode it as a Lehmer code. We will prove that these maps construct an equivalence
between the types $\Lehmer[n]$ and $\Aut[\Fin[\suc[n]]]$.~\footnote{Note that the permutations are off-by-one, because
we ignored the 0-position in the Lehmer code.}

@@

\begin{appendixproof}
  The first and second propositions follow from simply constructing the bijections using the decidable equality of
  $\Fin[n]$, and making sure to punch-in and punch-out the element $k$ at the right place.

@@

  For the other direction, if we are given a $k$ and a bijection $\pi$ between $\FinExcept{\suc[n]}[n]$ and
  $\FinExcept{\suc[n]}[n - k]$, we can extend $\pi$ to $\sigma : \Fin[\suc[n]] \eqv \Fin[\suc[n]]$ by inserting the
  element $n$ at the position $n - k$, resulting in the element $n$ having inversion count $k$.
\end{appendixproof}

@@

By composing~\cref{prop:lehmer-aut-equiv} and~\cref{prop:sn-im-lehmer-equiv}, we obtain the final equivalence.
